The problem and promise of scale in multilayer animal social networks

### 2020-02-12 paper/manuscript.Rmd
fst win pos

**Missing: discussion of window position..**

>>>>

Moving winter and summer seasons showed increasing connectivity of individuals. Graph strength and layer relevance increased at time window position ~20 for summer layers (Figure \@ref(fig:winpos)a, Figure \@ref(fig:winpos)b). Layer similarity... <!-- TODO: between
seasons increased consistently across landcover class (Figure
\@ref(fig:winlen)b).--> Connective redundancy was stable throughout the shifting window positions (Figure \@ref(fig:winpos)). Similar to window length, increasing window position results in a mismatch between expected periods of resource seasonality and corresponding sociality.
